Compiling refinement types to dependent types

### 2020-07-05 tex/paper.tex
Theorem command definition
Write a bit more about oracle translation assumptions

@@

The translation function $[|\ |]$ maps the typing context $\nonterm G$ to some logic.
In the subsequent text we assume the oracle can decide the resulting proposition
(otherwise it might be left as a separate lemma to be filled out by the user in the core language, or rejected altogether).

For the example oracle being an SMT solver and the syntax of terms also including mathematics, $[|\ |]$ might be defined as
\begin{equation}
\begin{aligned}
  & [| \emptyset |]                                         && \triangleq \top																						 \\
  & [| \nonterm G, x : \{ v : \nonterm B | \nonterm r \} |] && \triangleq [| \nonterm G |] \land [| \{x/v\} \nonterm r |] \\
  & [| \nonterm r_1 \land \nonterm r_2 |]                   && \triangleq [| \nonterm r_1 |] \land [| \nonterm r_2 |]		 \\
  & \cdots TODO
\end{aligned}
\end{equation}

@@

>>>>

\newtheorem{theorem}{Theorem}

@@

The translation function $[|\ |]$ maps the typing context $\nonterm G$ to some logic:
\begin{equation}
\begin{aligned}
  & [| \emptyset |]                                         && \triangleq \top																						\\
  & [| \nonterm G, x : \{ v : \nonterm B | \nonterm r \} |] && \triangleq [| \nonterm G |] \land [| \{x/v\} \nonterm r |] \\
  & [| \nonterm r_1 \land \nonterm r_2 |]                   && \triangleq [| \nonterm r_1 |] \land [| \nonterm r_2 |]		  \\
  & [| \nonterm{es} |]                                      && \triangleq \text{oracle}(\nonterm{es})                     \\
  & [| \nonterm{es}_1 = \nonterm{es}_2 |]                   && \triangleq \text{oracle}(\nonterm{es}_1 = \nonterm{es}_2)  \\
\end{aligned}
\end{equation}

The last two equations represent the assumption
that the oracle knows how to translate the elementary refinements being the terms $\nonterm{es}$
or equality propositions $\nonterm{es}_1 = \nonterm{es}_2$.

@@

In the subsequent text we also assume the oracle can decide the resulting proposition
(otherwise it might be left as a separate lemma to be filled out by the user in the core language, or rejected altogether).
